Type-safe client-server communication in functional web applications

### 2014-03-01 paper.tex
Explain that "no compiler support" means that we need a HS2JS compiler.

Several attempts have been made at tackling this problem, but none is, in our
view, satisfactory. In this paper, we propose a functional programming model in
which a web application is written as a single program from which client and
server binaries are generated during compilation. Type annotations in the source
program control which parts are executed on the server and which are executed
on the client, and the two communicate using type safe RPC calls. Functions
which are not explicitly declared as server-side or client-side are usable by
either side. Our solution is implemented as a Haskell library requiring minimal
to no compiler support, ensuring portability and modularity.

As our implementation depends on the Haste Haskell to Javascript compiler, this
paper also goes into some detail about its design and implementation.

>>>>

Several attempts have been made at tackling this problem, but none is, in our
view, satisfactory. In this paper, we propose a functional programming model in
which a web application is written as a single program from which client and
server binaries are generated during compilation. Type annotations in the source
program control which parts are executed on the server and which are executed
on the client, and the two communicate using type safe RPC calls. Functions
which are not explicitly declared as server-side or client-side are usable by
either side.

Recent advances in compiler technology from functional languages to Javascript
have led to a wealth of compilers targeting the web space, and enabled the
practical development of functional libraries and applications for
the browser. This enables us to implement our solution as a simple Haskell
library for any compiler capable of producing Javascript output, requiring no
further modification to existing compilers.

As our implementation targets the Haste Haskell to Javascript compiler, this
paper also goes into some detail about its design and implementation as well
as the alternatives available for compiling functional languages to a browser
environment.
